Typed Functional Genetic Programming

### 2013-07-21 tex/thesis.tex
[tex]

\section{Program trees}

@@

@@

In this chapter we briefly describe key concepts
from simply typed $\lambda$-calculus.
We try to favor readability over formality,
for more detailed and formal treatment of this subject see 
\cite{barendregt92}.

After that, \textit{inhabitation tree} is introduced.
It is structure used for reasoning about generation of individuals.

@@

Now we will formally describe programming language 
in which we will generate individual programs --- so called \lterms.

@@

Let $V$ be infinite countable set of {\it 
variable names}. Let $C$ be set of {\it constant names}, 
$V \cap C = \emptyset$.	 	
Then $\Lambda$ is set of {\it \lterms} defined inductively as follows.	
\begin{align*}
x   \in V \cup C  &\then x     \in \Lambda \\
M,N \in \Lambda   &\then (M~N) \in \Lambda 
\textit{~~~~~~(Function application)} \\
x   \in V , M \in \Lambda &\then \lamb{x}{M} \in \Lambda
\textit{~~~~~($\lambda$-abstraction)} 
\end{align*}~
\end{definition}

@@

Examples of \lterms:

\begin{easylist}[itemize]
& $x$
& $\lamb{x}{x}$
& $\lamb{x}{f}$
& $(\lamb{x}{(x~x)}~\lamb{x}{(x~x)})$
& $\lamb{x}{\lamb{y}{x}}$
& $\lamb{f}{\lamb{g}{\lamb{x}{((f~x)~(g~x))}}}$
\end{easylist}~

We use following notation
abbreviations for better readability:

\begin{easylist}[itemize]
& $M_1~M_2~M_3~\dots~M_n$ for 
  $(\dots((M_1~M_2)~M_3)~\dots~M_n)$ 
& $\lam{x_1 x_2 \dots x_n }{M}$ for
  $\lamb{x_1}{\lamb{x_2}{\dots\lamb{x_n}{M}\dots}}$
\end{easylist}~

@@

@@

\begin{todo}
& !!!!!!! zmínit $=_\beta$ a $\twoheadrightarrow_\beta$  a i pro ostatní redukce!!!!!
& definovat \textbf{CR} a říct o tom lemátku, že má CR redukce má unikátní nf.
\end{todo}

@@

\section{Types}
\label{deftype}

@@

@@

\begin{todo}
   & buď dokázat ty převody na grammar rules explicitně
     nebo říct že se to dokáže podobnym stylem jako v dukazu 
     v sekci \ref{barlike}
   & možná ocitovat toho van Wijngaarden [1981] s těma 2-level grammar
     jak je to v Barendregtovi \cite{barendregt10} 
   & vyřešit jak je to stou freš proměnnou x v introdukci...
     && stejně tak v tom obecnym případě to dělá neplechu
\end{todo}

@@

\begin{definition}
Let \GMS where 
$\sigma = \tau_1 \ar \dots \ar \tau_n \ar \alpha$,
$n \geq 0$.
Then $M$ is in \textit{long normal form} (\textit{lnf}) if following 
conditions are satisfied.
\begin{enumerate}
 \item $M$ is term of the form $\lam{x_1 \dots x_n}{f~M_1~\dots~M_m}$\\
  (specially for $n = 0$, $M$ is term of the form $f$),
 \item each $M_i$ is in \textit{long normal form}.
\end{enumerate}
\end{definition}~

As is shown in \cite{barendregt10} long normal form has those 
nice properties:

\begin{easylist}[itemize]
& Every $M$ in $\beta$-normal form has a long normal form 
$N$ such that $N \twoheadrightarrow_{\eta} M$.
& \textbf{TODO jen zkopčeno přepsat!!} .. if M has a beta-nf, which according to Theorem 2B.4 is
always the case, then it also has a unique lnf and this will be its unique $\beta\eta^{-1}$-nf.
& \textbf{TODO : potřebuju eštěnějaký z tyhle knihy?}
\end{easylist}

\begin{todo}
 & v barendrechtovi je to v definici lnf $\lam{x_1 \dots x_n}{f~M_1~\dots~M_n}$ místo 
   $M_m$ ale to musí bejt určitě překlep...
 & popsat tu jak ji předelat na beta nf
	pokud by se nám chtělo... 
	V barendrech84 (ta nová kniha s žlutejma deskama) je ukázano že je 
	eta CR (čurč roserovská) což snad stačí společně s 
	tim tvrzeničkem z book.pdf že vezmu lnf
	a dělám eta redukce dokud to de. až to nejde tak bych to měl mít v 
	beta-nf
 & přepsat to nějak hezčejc, ten seznam heskejch vlastností
\end{todo}

@@

In \cite{barendregt10} is shown term generating grammar with 
following rules (our notation is used, but we will not 
highlighted terminals anymore).\footnote{
I was using term generating grammars for term generation
on my own before I encountered with \cite{barendregt10},
where i happily discovered that Barendregt is using
almost identical notation.
}
\begin{align*}
( \alpha , \Gamma )  
&\gar
(~f~( \rho_1 , \Gamma )~\dots~( \rho_m , \Gamma )~)
& \textbf{if } \alpha \in A,
(f : \rho_1 \ar \dots \ar \rho_m \ar \alpha) \in \Gamma
\\ 
( \sigma \rightarrow \tau , \Gamma )  
&\gar
(~\lambda~x~.~( \tau ; \Gamma,x:\sigma )~)
&   
\end{align*}

@@

@@

$\IT(\sigma,\Gamma) = $ \\

@@

$\IT(\sigma,\Gamma) =$\\

@@

\section{Tree representations of \lterms}
\label{tree-reps}

From the definition of \lterm (\ref{deflam}) we can straightforwardly derive 
the classical tree representation for \lterms. Term M is translated into tree $T[M]$ by following rules:

\begin{itemize}
	\item $x \in V \cup C$ translates into \textit{leaf} $x$.
	\item $(P$ $Q)$ translates into tree\\
		\Tree
			[.@	
		 		\text{$T[P]$}
		 		\text{$T[Q]$}		 			
			] 
	\item $\lambda x . P$ translates into tree\\
	 	\Tree
			[.\text{$\lambda x$}	
		 	 	\text{$T[P]$}	
			] 
\end{itemize}

We can enhance this representation by compressing consecutive lambda abstractions into one
tree node like this:

\begin{itemize}
	\item $\lambda x_1 \dots x_n . P$ translates into tree\\
	 	\Tree
			[.\text{$\lambda x_1 \dots x_n$ }	
		 	 	\text{$T[P]$}	
			] 
\end{itemize}

As this representation comes directly from definition it is evident 
that it covers all possible \lterms.

We will refer to this representation as to \textit{\atTree}.\\

For representing expressions as trees it is however more common to use a little different
representation. It will also be the representation suitable for showing 
that \textit{solving} Inhabitation tree generates wanted \lterm.

\begin{itemize}
    \item $x \in V \cup C$ translates into \textit{leaf} $x$.
	\item $(f M_1 M_2 \dots M_n)$ where $f \in V \cup C, n \geq 1$ translates into tree\\
		\Tree
			[.f	
		 		\text{$T[M_1]$}
		 		\text{$T[M_2]$}
		 		\text{$\dots$}
		 		\text{$T[M_n]$}		 				 			
			] 
	\item $\lambda x_1 \dots x_n . M$ translates into tree\\
	 	\Tree
			[.\text{$\lambda x_1 \dots x_n$ }	
		 	 	\text{$T[M]$}	
			] 
\end{itemize}

Notice that this representation does not cover all \lterms, 
e.g. $(\lambda x.x) y$ is not expressible in it. But it does not bother us.

We will refer to this representation as to \textit{\sexprTree}.\\

\Lets now consider representation for \textit{typed \lterms}.
Straightforward approach would be to add to each node a type entry which 
would be the type of the \lterm corresponding to subtree having this
node as the root node.

Approach more suitable for our purpose is to add a special type node above each node.
More specifically:

\Lets consider tree $t$ corresponding to a \lterm of a type
$\sigma$ with root $r$ and subtrees $s_1 , \dots , s_n$. 
Then corresponding tree $TT[t]$ for typed \lterm is 
obtained from the tree $t$ as follows:

@@

\bibitem{koza92}

  John R. Koza,
  \emph{Genetic Programming: On the Programming of Computers by Means of Natural Selection}.
  MIT Press, Cambridge, MA,
  1992.

\bibitem{koza05}

  Koza, J.R., Keane, M., Streeter, M., Mydlowec, W.,Yu, J., Lanza, G. 
  \emph{Genetic Programming IV: Routine Human-Competitive Machine Intelligence.} 
  Springer, 2005. ISBN 978-0-387-26417-2

\bibitem{yu01}

  T. Yu. 
  \emph{Hierachical processing for evolving recursive and modular 
        programs using higher order functions and lambda abstractions}. 
  Genetic Programming and Evolvable Machines,
  2(4):345–380, December 2001. ISSN 1389-2576.

\bibitem{montana95}

D. J. Montana. 
\emph{Strongly typed genetic programming.} 
Evolutionary Computation, 3(2): 199–230, 1995.
%URL \url{ http://vishnu.bbn.com/papers/stgp.pdf }. nefacha

\bibitem{haynes96}

T. D. Haynes, D. A. Schoenefeld, and R. L. Wainwright. 
\emph{Type inheritance in strongly typed genetic programming.} 
In P. J. Angeline and K. E. Kinnear, Jr., editors, Advances
in Genetic Programming 2, chapter 18, pages 359–376.
MIT Press, Cambridge, MA, USA, 1996. ISBN 0-262-01158-1.\\ 
URL 
\url{http://www.mcs.utulsa.edu/~rogerw/papers/Haynes-hier.pdf}.

\bibitem{olsson94}

J. R. Olsson. 
\emph{Inductive functional programming using incremental program 
transformation and Execution of logic programs by 
iterative-deepening A* SLD-tree search.} 
Dr scient thesis, University of Oslo, Norway, 1994.

\bibitem{barendregt92}
H. Barendregt , S. Abramsky , D. M. Gabbay , T. S. E. Maibaum , H.  P.
\emph{Lambda Calculi with Types.} 
Handbook of Logic in Computer Science, 1992.

@@

\bibitem{AIAMA}

	Stuart J. Russell, Peter Norvig,
	\emph{Artificial Intelligence: A Modern Approach}.
	Pearson Education,
	2003.

@@

>>>>

\section{Program trees}
\label{GP-prog-trees}

@@

\begin{todo}
 & nějak to tu přepsat aby to bylo ve stejnym stylu jako v \ref{tree-reps}
\end{todo}

@@

In this chapter we briefly describe key concepts
of simply typed $\lambda$-calculus.
We try to favor readability over formality,
for more detailed and formal treatment of this subject see 
\cite{barendregt92,barendregt10}.

After introductory description, an analysis of term generation follows; 
a path from inference rules to term generating grammar rules is shown,
\textit{long normal form (lnf)} is described,
followed by term generating grammar for \textit{lnf}
and analysis of its relevant properties (such as its relation to \benf),
then \textit{inhabitation tree} is presented --- 
an implementation friendly refinement of 
\textit{lnf} term generating grammar.

\begin{todo}
 & Až to bude dostatečně sepsáno, tak do této kapitoly taky přidat
   část o abstraction elimination a o polymorfním zobecnění inhabitation tree.
   Nezapomenout to pak zmínit i v tomhle úvodu.
\end{todo}

@@

Here we  %formally 
describe programming language, 
in which we generate individual programs --- so called \lterms.

@@

Let $V$ be infinite countable set of {\it 
variable names}. Let $C$ be set of {\it constant names}, 
$V \cap C = \emptyset$.	 	
Then $\Lambda$ is set of {\it \lterms} defined inductively as follows.	
\begin{align*}
x   \in V \cup C  &\then x     \in \Lambda \\
M,N \in \Lambda   &\then (M~N) \in \Lambda 
\textit{~~~~~~(Function application)} \\
x   \in V , M \in \Lambda &\then \lamb{x}{M} \in \Lambda
\textit{~~~~($\lambda$-abstraction)} 
\end{align*}~
\end{definition}

@@

We use following notation
abbreviations for better readability. \vspace{3mm}

\begin{easylist}[enumerate]
& $M_1~M_2~M_3~\dots~M_n$ for 
  $(\dots((M_1~M_2)~M_3)~\dots~M_n)$ 
& $\lam{x_1 x_2 \dots x_n }{M}$ for
  $\lamb{x_1}{\lamb{x_2}{\dots\lamb{x_n}{M}\dots}}$
\end{easylist}~

@@

\newcommand{\ods}{\hspace{3mm}}

Here follow some examples of \lterms. \vspace{1mm}

\ods $x$

\ods $\lamb{x}{x}$

\ods $\lamb{x}{f}$

\ods $(\lamb{x}{(x~x)}~\lamb{x}{(x~x)})$

\ods $\lamb{x}{\lamb{y}{x}}$

\ods $\lamb{f}{\lamb{g}{\lamb{x}{((f~x)~(g~x))}}}$

@@

\begin{todo}
& asi to přepsat nějak obecně pro redukci R a pak zadat beta,eta,eta-1 
  jako specialni připady
& !!!!!!! zmínit $=_\beta$ a $\twoheadrightarrow_\beta$  a i pro ostatní redukce!!!!!
& definovat \textbf{CR} a říct o tom lemátku, že má CR redukce má unikátní nf.
&& V \cite{barendregt84} (ta nová kniha s žlutejma deskama) je ukázano že je 
	 eta CR (Church Rosserovská)
& zmínit Theorem 2B.4 z \cite{barendregt10}
& co to znamená mít nf
\end{todo}

@@

\subsection{Tree representations of \lterms}
\label{tree-reps}

From the definition of \lterm we can straightforwardly derive 
the standard tree representation for \lterms, which we call 
\textit{\atTree}. Term M is 
translated into \atTree $T_@[M]$ by following rules.

\begin{enumerate}
	\item $T_@[x] := x$ (i.e. $x \in V \cup C$ becomes one node tree $x$)
	\item \mbox{$T_@[(P$ $Q)] := $ \Tree
			[.@	
		 		\text{$T_@[P]$}
		 		\text{$T_@[Q]$}		 			
			] }
	\item \mbox{$T_@[\lambda x . P] := $ \Tree
			[.\text{$\lambda x$}	
		 	 	\text{$T_@[P]$}	
			] }
\end{enumerate}

We can enhance this representation by replacing third rule
by following one. It compressing consecutive 
$\lambda$-abstractions into one \atTree node. \\

\mbox{$T_@[\lambda x_1 \dots x_n . P] := $ \Tree
	[.\text{$\lambda x_1 \dots x_n$ }	
 	 	\text{$T_@[P]$}	
	] }

Since this representation comes directly from definition, 
it is evident that it covers all possible \lterms.\\

Following tree representation is extension of 
\textit{S-expression trees} described in~\ref{GP-prog-trees},
thus we call it \textit{\sexprTree}.
Unlike \atTree, it is not able to cover all \lterms, but only those
in \bnf. 
Term M is translated into \sexprTree $T_S[M]$ by following rules.

%It will also be the representation suitable for showing 
%that \textit{solving} Inhabitation tree generates wanted \lterm.

\begin{enumerate}
    \item $T_S[x] := x$
	\item \mbox{ $T_S[(f M_1 M_2 \dots M_m)] := $ 
	%where $f \in V \cup C, n \geq 1$ translates into tree\\
		\Tree
			[.f	
		 		\text{$T_S[M_1]$}
		 		\text{$T_S[M_2]$}
		 		\text{$\dots$}
		 		\text{$T_S[M_m]$}		 				 			
			] }
	\item \mbox{$T_S[\lambda x_1 \dots x_n . M] := $
	 	\Tree
			[.\text{$\lambda x_1 \dots x_n$ }	
		 	 	\text{$T_S[M]$}	
			] }
\end{enumerate}~

 & zkontrolovat že reference tree-reps se odkazuje na dobrý místo,
   mohlo by se to rozbít tim že tree reprezentations - typovany/netypovany 
   jsou od sebe oddelený
\end{todo}

\newpage
\section{Types}
\label{deftype}

@@

\subsection{Tree representations of typed \lterms}

\newcommand{\lsCurry}{$\lambda^{\ar}$\nobreakdash-Curry\xspace}
\newcommand{\lsChurch}{$\lambda^{\ar}$\nobreakdash-Church\xspace}

Simply typed $\lambda$-calculus as described above is formally
called the \textit{system \lsCurry}. 
Other slightly different formalization is called 
\textit{system \lsChurch}. 
They differ in that \lsCurry uses as terms above described
untyped terms, whereas \lsChurch uses slightly modified
terms with information about types of variables written in
lambda abstraction along with variable name.
Since those systems are proven to be equivalent,
we are not giving this subject much attention here.
For more detailed information on this subject see \cite{barendregt92}.\\

In our implementation we also use modified representation of \lterms
storing information about types. But our representation is more 
radical than that of \lsChurch; it stores information about types
of all subterms.

Regarding tree representation of such a typed
\lterm, most of the time it is more convenient to 
understand this information as invisibly sitting
in the tree nodes alongside with visible
term symbols.

But as we will see below in the section about \textit{inhabitation trees},
there are situations when the explicit type information in the tree representation
comes in handy. Thus we are presenting following tree representation.\\

Straightforward approach would be to add to each node a visible type entry 
that would be the type of the subterm corresponding to subtree having this
node as the root node.

Approach more suitable for our further purpose 
is to add a special type node \textit{above} each node.

More specifically,
\lets consider \textit{\sexprTree} $t$ corresponding to a \lterm of the type
$\sigma$ with root $r$ and subtrees $s_1 , \dots , s_n$. 
Then corresponding \textit{typed \sexprTree} $TT_S[t]$ for typed \lterm is 
obtained from the tree $t$ as follows.

We silently suppose here that type information about every subterm is available.

\begin{todo}
 & možná konec týhle subsekce trochu přeformulovat, je to takový kostrbatý...
\end{todo}

@@

\begin{todo}
   & buď dokázat ty převody na grammar rules explicitně
     nebo říct že se to dokáže podobnym stylem jako v dukazu 
     v sekci \ref{barlike}
   & možná ocitovat toho van Wijngaarden [1981] s těma 2-level grammar
     jak je to v Barendregtovi \cite{barendregt10} 
   & vyřešit jak to tu popsat s tou freš proměnnou x v introdukci...
     && stejně tak v tom obecnym případě to dělá neplechu
\end{todo}

@@

%v barendrechtovi je to v definici lnf
%$\lam{x_1 \dots x_n}{f~M_1~\dots~M_n}$ místo $M_m$ 
%ale to musí bejt určitě překlep...

\begin{definition}
Let \GMS where 
$\sigma = \tau_1 \ar \dots \ar \tau_n \ar \alpha, n \geq 0$.
	\begin{enumerate}
	  \item	
		Then $M$ is in \textit{long normal form} (\lnf) if following 
		conditions are satisfied.
		\begin{enumerate}
		 \item $M$ is term of the form $\lam{x_1 \dots x_n}{f~M_1~\dots~M_m}$\\
		  (specially for $n = 0$, $M$ is term of the form $f$).
		 \item Each $M_i$ is in \lnf.
		\end{enumerate}	
	  \item 
	    $M$ has a \lnf if $M =_{\beta\eta} N$ and $N$ is in \lnf.
	\end{enumerate}
\end{definition}~

As is shown in \cite{barendregt10}, \lnf has following nice properties.

\begin{proposition}
If $M$ has a \bnf, 
%which according to Theorem 2B.4 is always the case, 
then it also has a unique \lnf, 
which is also its unique \beenf.
\end{proposition}

\begin{proposition}
Every $B$ in \bnf has a \lnf 
$L$ such that $L \twoheadrightarrow_{\eta} B$.
\end{proposition}

\begin{todo}
 & co to znamená mít lnf
 & potřebuju eště nějaký \textbf{propositions} z tyhle knihy?
 & ta definice je tam daná pro $\tur{}{M}{\sigma}$,
   ukazat ze ta naše je ok, že tam má navíc to $\Gamma$.
   Stačí udělat tríček že beru funkci co má lambda hlavu odpovídající 
   tomu kontextu.
\end{todo}

@@

In \cite{barendregt10} is shown term generating grammar with 
following rules (our notation is used, but we will not 
highlighted terminals anymore).\footnote{
I was using term generating grammars for term generation
on my own before I encountered with \cite{barendregt10},
where i happily discovered that Barendregt is using
almost identical notation. 
But his \lnf grammar was more clever then my grammar
that was using grammar rules corresponding to the three basic
inference rules. 
}
\begin{align*}
( \alpha , \Gamma )  
&\gar
(~f~( \rho_1 , \Gamma )~\dots~( \rho_m , \Gamma )~)
& \textbf{if } \alpha \in A,
(f : \rho_1 \ar \dots \ar \rho_m \ar \alpha) \in \Gamma
\\ 
( \sigma \rightarrow \tau , \Gamma )  
&\gar
(~\lambda~x~.~( \tau ; \Gamma,x:\sigma )~)
&   
\end{align*}

@@

\begin{todo}
 & zmínit že podobně jako mužeme transformovat inference rules
   na grammar rules, mužeme i obráceně grammar rules
   převést na inference rules - to bylo ostatně uděláno v tom dukazu ale
   je to podle mě hezký říct ty pravidla explicitně.
\end{todo}

@@

$\IT(\sigma,\Gamma) := $ \\

@@

$\IT(\sigma,\Gamma) := $\\

@@

@@

\bibitem{koza92}
  John R. Koza,
  \emph{Genetic Programming: On the Programming of Computers by Means of Natural Selection}.
  MIT Press, Cambridge, MA,
  1992.

\bibitem{koza05}
  Koza, J.R., Keane, M., Streeter, M., Mydlowec, W.,Yu, J., Lanza, G. 
  \emph{Genetic Programming IV: Routine Human-Competitive Machine Intelligence.} 
  Springer, 2005. ISBN 978-0-387-26417-2

\bibitem{yu01}
  T. Yu. 
  \emph{Hierachical processing for evolving recursive and modular 
        programs using higher order functions and lambda abstractions}. 
  Genetic Programming and Evolvable Machines,
  2(4):345–380, December 2001. ISSN 1389-2576.

\bibitem{montana95}
D. J. Montana. 
\emph{Strongly typed genetic programming.} 
Evolutionary Computation, 3(2): 199–230, 1995.
%URL \url{ http://vishnu.bbn.com/papers/stgp.pdf }. nefacha

\bibitem{haynes96}
T. D. Haynes, D. A. Schoenefeld, and R. L. Wainwright. 
\emph{Type inheritance in strongly typed genetic programming.} 
In P. J. Angeline and K. E. Kinnear, Jr., editors, Advances
in Genetic Programming 2, chapter 18, pages 359–376.
MIT Press, Cambridge, MA, USA, 1996. ISBN 0-262-01158-1.\\ 
URL 
\url{http://www.mcs.utulsa.edu/~rogerw/papers/Haynes-hier.pdf}.

\bibitem{olsson94}
J. R. Olsson. 
\emph{Inductive functional programming using incremental program 
transformation and Execution of logic programs by 
iterative-deepening A* SLD-tree search.} 
Dr scient thesis, University of Oslo, Norway, 1994.

\bibitem{barendregt84}
H. P. Barendregt,
\emph{The Lambda Calculus: its Syntax and Semantics}, 
revised ed., North-Holland, 1984.

\bibitem{barendregt92}
H. Barendregt , S. Abramsky , D. M. Gabbay , T. S. E. Maibaum.
\emph{Lambda Calculi with Types.} 
Handbook of Logic in Computer Science, 1992.

@@

\bibitem{AIAMA}
	Stuart J. Russell, Peter Norvig,
	\emph{Artificial Intelligence: A Modern Approach}.
	Pearson Education,
	2003.

@@

%\section{---OLD---Tree representations of \lterms}

%From the definition of \lterm (\ref{deflam}) we can straightforwardly derive 
%the classical tree representation for \lterms. Term M is translated into tree $T[M]$ by following rules:
%
%\begin{itemize}
%	\item $x \in V \cup C$ translates into \textit{leaf} $x$.
%	\item $(P$ $Q)$ translates into tree\\
%		\Tree
%			[.@	
%		 		\text{$T[P]$}
%		 		\text{$T[Q]$}		 			
%			] 
%	\item $\lambda x . P$ translates into tree\\
%	 	\Tree
%			[.\text{$\lambda x$}	
%		 	 	\text{$T[P]$}	
%			] 
%\end{itemize}
%
%We can enhance this representation by compressing consecutive lambda abstractions into one
%tree node like this: 
%
%\begin{itemize}
%	\item $\lambda x_1 \dots x_n . P$ translates into tree\\
%	 	\Tree
%			[.\text{$\lambda x_1 \dots x_n$ }	
%		 	 	\text{$T[P]$}	
%			] 
%\end{itemize}
%
%As this representation comes directly from definition it is evident 
%that it covers all possible \lterms.
%
%We will refer to this representation as to \textit{\atTree}.\\
% 
%
%For representing expressions as trees it is however more common to use a little different
%representation. It will also be the representation suitable for showing 
%that \textit{solving} Inhabitation tree generates wanted \lterm.
%
%\begin{itemize}
%    \item $x \in V \cup C$ translates into \textit{leaf} $x$.
%	\item $(f M_1 M_2 \dots M_n)$ where $f \in V \cup C, n \geq 1$ translates into tree\\
%		\Tree
%			[.f	
%		 		\text{$T[M_1]$}
%		 		\text{$T[M_2]$}
%		 		\text{$\dots$}
%		 		\text{$T[M_n]$}		 				 			
%			] 
%	\item $\lambda x_1 \dots x_n . M$ translates into tree\\
%	 	\Tree
%			[.\text{$\lambda x_1 \dots x_n$ }	
%		 	 	\text{$T[M]$}	
%			] 
%\end{itemize}
%
%Notice that this representation does not cover all \lterms, 
%e.g. $(\lambda x.x) y$ is not expressible in it. But it does not bother us. 
%
%We will refer to this representation as to \textit{\sexprTree}.\\ 
%
%\Lets now consider representation for \textit{typed \lterms}.
%Straightforward approach would be to add to each node a type entry which 
%would be the type of the \lterm corresponding to subtree having this
%node as the root node. 
%
%Approach more suitable for our purpose is to add a special type node above each node.
%More specifically:
%
%\Lets consider tree $t$ corresponding to a \lterm of a type
%$\sigma$ with root $r$ and subtrees $s_1 , \dots , s_n$. 
%Then corresponding tree $TT[t]$ for typed \lterm is 
%obtained from the tree $t$ as follows:  
%
%\begin{equation*}
%\mbox{ 
%TT[
%\Tree
%	[.r 	
%	  	  \text{$s_1$}
%		  \text{$s_2$}
%		  \text{$\dots$}
%		  \text{$s_n$}
%	] 
%}]=
%\mbox{
%\Tree
%	[.\text{$\sigma$ }
%	    [.r 	
%	  	  \text{$TT[s_1]$}
%		  \text{$TT[s_2]$}
%		  \text{$\dots$}
%		  \text{$TT[s_n]$}
%		]	  	
%	] 
%}
%\end{equation*}
